animbook: Visualizing Changes in Performance Measures and Demographic Affiliations using Animation

### 2025-07-11 animbook-journal.Rmd
fixed redundancy comment
proportional shade comment
wallaby plot not wallabys plot

  @mayer_2005 states that designing multimedia requires the designer to understand how people learn. One of the principles in @mayer_2005, Redundancy, suggests that a piece of excess information could overload the learners. By this principle, the animation must be carefully designed to avoid this pitfall.

@@

  The `wallaby_data()` function is responsible for performing data manipulation and formatting tasks on the original object. It includes creating additional data components for labeling and shading. This function is also responsible for interpolating the non-linear path. It performs this task by mapping the `sine()` function provided in this package to each observation using the `map()` function from the \CRANpkg{purrr} package (@purrr). The frame is recalculated using the same method mentioned in the data preprocessing section. The `proportional_shade()` function is called to generate the proportional shaded data.

  The `proportional_shade()` function's algorithm begins by calculating the corner points for each shaded area. Subsequently, the algorithm utilizes the `sine()` function to interpolate points between the left and right boundaries. Once this interpolation is completed, all the generated points are interconnected to form the shaded regions.

@@

  Now that the data are in the right format for the wallaby's plot, the `geom_point()` function is used for plotting the observations, `geom_polygon()` is used for creating the proportional shaded areas, and `geom_text()` is used for creating labels. These three functions are from the \CRANpkg{ggplot2} package. During this process, the aesthetics mapping will be different depending on the rendering tool to be used, which can be either `gganimate` or `plotly`. The difference between the two rendering tools is that for `plotly`, the `ids` and `frame` arguments need to be specified during the creation of the `ggplot` object.

>>>>

  @mayer_2005 states that designing multimedia requires the designer to understand how people learn. One of the principles in @mayer_2005,  redundancy, suggests that a piece of excess information could overload the learners. By this principle, the animation must be carefully designed to avoid this pitfall.

@@

  The `wallaby_data()` function is responsible for performing data manipulation and formatting tasks on the original object. It includes creating additional data components for labeling and shading. This function is also responsible for interpolating the non-linear path. It performs this task by mapping the `sine()` function provided in this package to each observation using the `map()` function from the \CRANpkg{purrr} package (@purrr). The frame is recalculated using the same method mentioned in the data preprocessing section.

  The `proportional_shade()` function is called to generate the proportional shaded data. The `proportional_shade()` function's algorithm begins by calculating the corner points for each shaded area. Subsequently, the algorithm utilizes the `sine()` function to interpolate points between the left and right boundaries. Once this interpolation is completed, all the generated points are interconnected to form the shaded regions.

@@

  Now that the data are in the right format for the wallaby plot, the `geom_point()` function is used for plotting the observations, `geom_polygon()` is used for creating the proportional shaded areas, and `geom_text()` is used for creating labels. These three functions are from the \CRANpkg{ggplot2} package. During this process, the aesthetics mapping will be different depending on the rendering tool to be used, which can be either `gganimate` or `plotly`. The difference between the two rendering tools is that for `plotly`, the `ids` and `frame` arguments need to be specified during the creation of the `ggplot` object.
